### 2015-01-19 src/discussion.Rnw
update t-test table

\subsubsection{Operator Selection}
From Table~\ref{tbl:selective}, we see that except for statement deletion, we
have negative utility in comparison to baseline for both tests and asserts.
Even for statement deleition, the utility is just 0.5 tests better than
baseline. A similar result is present in the strategy effectiveness also,
where the effectiveness over baseline is either negettive or extremely small.

>>>>

\subsubsection{Operator Selection}
From Table~\ref{tbl:selective}, looking at the test and assert utility,
we see that there are a few selective strategies that seem to score a positive
test utility. Notably, the statement modification strategy sselective does
about 1.86\% better than the random selection for test utility, and has similar
advantage in assert utility. It also seem to have a slight advantage of 0.27\%
in the strategy effectivenss.

The statistical analysis in Table~\ref{tbl:ttests}

### 2015-01-19 src/ttests.Rnw
update t-test table

>>>>

db <- subset(common.db, operator=="sselective")
sselective.t <- mintc.t.test(db)
sselective.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rselective")
rselective.t <- mintc.t.test(db)
rselective.m <- mutant.t.test(db)

db <- subset(common.db, operator=="esselective")
esselective.t <- mintc.t.test(db)
esselective.m <- mutant.t.test(db)

db <- subset(common.db, operator=="reselective")
reselective.t <- mintc.t.test(db)
reselective.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rsselective")
rsselective.t <- mintc.t.test(db)
rsselective.m <- mutant.t.test(db)
